Free surface computations in mantle convection models

### 2015-11-02 free-surface-paper.tex
Add some text on refinement

We also investigate the advantages of combining adaptive mesh refinement with free surface computations.
\citet{crameri2012comparison} performed a community benchmark of a setup for which there is no analytic
solution. In this benchmark, a buoyant blob rises beneath a viscous lid with a free surface, deflecting the
boundary upwards (for the full setup, see \citet{crameri2012comparison}). 
Figure~\ref{fig:amr} shows the convergence of the maximum topography at 3 Myr to its value in a high resolution simulation.
Figure~\ref{fig:amr}a shows the convergence with uniform refinement, and~\ref{fig:amr}b shows the convergence
with adaptive mesh refinement. Both have essentially the same behavior, but the adaptive case requires 
fewer degrees of freedom by a factor of approximately an order of magnitude. More complex models will have
more detail and so we may be less able to aggressively coarsen them, but we still expect that adaptive mesh refinement 
will result in significant computational savings.

>>>>

We also investigate the advantages of combining adaptive mesh refinement with free surface computations.
\citet{crameri2012comparison} performed a community benchmark of a setup for which there is no analytic
solution. In this benchmark, a buoyant blob rises beneath a viscous lid with a free surface, deflecting the
boundary upwards (for the full setup, see \citet{crameri2012comparison}). 
Figure~\ref{fig:amr} shows the convergence of the maximum topography at 3 Myr to its value in a high resolution simulation,
both with and without adaptive mesh refinement.
For the uniform refinement cases each point is generated by running the benchmark with a different global refinement level.
For the adaptive case each point is generated by allowing the mesh to be refined, where the maximum refinement level
is limited to the same refinement level of the corresponding global refinement simulation.
We refine every ten timesteps according to gradients in the density and compositional fields.

The convergence with and without adaptive mesh refinement have essentially the same behavior, but the adaptive case requires 
fewer degrees of freedom by a factor of approximately an order of magnitude. More complex models will have
more detail and so we may be less able to aggressively coarsen them, but we still expect that adaptive mesh refinement 
will result in significant computational savings.
